---
output: github_document
---

# recorderFeedback

**recorderFeedback** is an R package for generating personalised, data-driven feedback, originally designed for citizen science wildlife recording but adaptable to other domains. The package provides tools to set up a feedback workflow, load data, generate content, and distribute feedback to recipients.

## Features

- **Project Initialisation**: Quickly scaffold a new feedback project with all necessary files and folders.
- **Data Loading**: Import recipient and observation data from configurable sources.
- **Computation**: Run custom analyses or summaries on your data before generating feedback.
- **Content Rendering**: Create personalised feedback documents for each recipient using RMarkdown templates.
- **Batch Processing**: Automate feedback generation for multiple recipients.
- **Email Dispatch**: Send feedback via email using SMTP.

Package functions are prefixed with `rf_`.

## Installation

Install from GitHub using `devtools`:

```r
devtools::install_github("yourusername/recorderFeedback")
```

## Quick Start

```{r quick_start}
library(recorderFeedback)

#initialise a new project
rf_init(path = "example")
config <- config::get()

#get recipients
rf_get_recipients()
knitr::kable(head(read.csv(config$recipients_file)))

#get data
rf_get_data()
knitr::kable(head(read.csv(config$data_file)))

#render a single feedback item
rf_render_single(recipient_id = 1)

# run the pipeline
batch_id <- "test_batch"
rf_generate(batch_id)

#view the meta table
meta_table <- read.csv(file.path("renders",batch_id,"/meta_table.csv"))
knitr::kable(head(meta_table))

#look at the contents of one of the renders
print(readLines(meta_table$file[1]))

#send the emails
#rf_dispatch_smtp(batch_id)
```

## Workflow Overview

1. **Initialise Project**: Use `rf_init()` to create a new project structure.
2. **Configure**: Edit the configuration file to set paths and options.
3. **Load Data**: Import recipients and data using provided functions.
4. **Compute**: Optionally process data for summaries or statistics.
5. **Render Feedback**: Generate personalised feedback documents.
6. **Distribute**: Send feedback via email or other channels.

## Key terms:

 - Recipient: someone to receive feedback
 - Focal/background: whether the data relates to the recipient (focal), or not (background)
 - Template: a RMarkdown document defining how the data is manipulated and visualised
 - Computations: calculations or other processing done on the raw data prior to rendering them template

## Configuration

### General

`config.yml`

### Data sources (recipients)

`scripts/get_recipients.R`

### Data sources (records)

`scripts/get_data.R`

### Content (R)

`templates/content.Rmd`
`templates/email_format.R`

### Look and feel (HTML+CSS)

`templates/template.html`


### Pipeline

`_targets.R`
`run_pipeline.R`


```{r cleanup, echo = FALSE}
setwd("C:/Users/simrol/OneDrive - UKCEH/R_onedrive/R_2025/recorderFeedback")
unlink("example", recursive=TRUE)
```
