---
title: "Generating Content"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generating Content}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(recorderFeedback)
```

# Generating Content

This vignette explains how to turn your loaded data into personalised feedback pages.
It is aimed at new users who have already completed the "Getting Data" steps.

## Workflow At A Glance

The content stage has three parts:

1. Optional computations on focal and background data.
2. Rendering one recipient for testing.
3. Rendering all recipients as a batch.

## Configuration

Content generation is controlled by `config.yml`. Key entries are:

- `computation_script_focal`: Script for computations on focal (recipient-specific) data.
- `computation_script_bg`: Script for background computations.
- `recipient_select_script`: Optional script for selecting which recipients to render in a batch.
- `content_template_file`: RMarkdown template for rendering feedback.
- `html_template_file`: HTML template for styling output.

By default, both computation script fields point to `"scripts/computation.R"`.

```{r show_content_config}
config <- config::get()
config[c(
  "computation_script_focal",
  "computation_script_bg",
  "recipient_select_script",
  "content_template_file",
  "html_template_file"
)]
```

## Computations

Computation scripts let you prepare summaries and metrics before rendering.
This is useful for totals, rankings, trends, and other values you want to reuse in templates.

In normal use, computations are executed automatically as part of rendering.
If you are building custom scripts, this is the core helper used internally:

```{r run_computations}
records <- read.csv(config$data_file)
computed <- rf_do_computations(config$computation_script_bg, records)
```

Your computation script should define `compute_objects(records_data)` and return an object (often a list) that can be used in templates.

## Rendering Content

Start by rendering a single recipient to check template logic before running a full batch.

```{r render_single}
# Use a known recipient_id from recipients_file
rf_render_single(recipient_id = 1)
```

Then run the whole batch:

```{r generate_batch}
batch_id <- "example_batch"
rf_render_all(batch_id)
```

## Rendering Only Selected Recipients

Batch rendering can be filtered with the script referenced by `recipient_select_script`.
That script should define `recipient_select(recipients, data, config)` and return one of:

- `NULL` to render everyone.
- A logical vector with one value per row in `recipients`.
- A vector of `recipient_id` values to render.
- A data frame containing `recipient_id`, `selected`, and optional `skip_reason`.

For example, to render only recipients that have at least five records and record why others were skipped:

```{r recipient_select_example}
recipient_select <- function(recipients, data, config) {
  counts <- aggregate(list(n = data$recipient_id), by = list(recipient_id = data$recipient_id), FUN = length)
  counts <- merge(recipients["recipient_id"], counts, by = "recipient_id", all.x = TRUE)
  counts$n[is.na(counts$n)] <- 0

  data.frame(
    recipient_id = counts$recipient_id,
    selected = counts$n >= 5,
    skip_reason = ifelse(counts$n >= 5, NA_character_, "Fewer than 5 records"),
    stringsAsFactors = FALSE
  )
}
```

Skipped recipients remain in `renders/<batch_id>/meta_table.csv` with `render_status = "skipped"`, but no HTML file is produced for them.

## Using Location-Based Feedback Instead of Individual-Based Feedback

You can use `recorderFeedback` for place-based reporting (for example, "all species recorded in location X") rather than person-based reporting.

The main idea is:

1. Keep one row per email recipient in `recipients_file`.
2. Add location fields to recipients (for example `location_id`, `location_name`).
3. Ensure your records data includes a matching location field.
4. Change `scripts/focal_filter.R` so focal data is filtered by location, not by recorder identity.

Required recipient columns are still `recipient_id`, `name`, and `email`, but you can add any extra columns needed for filtering and template content.

Example `focal_filter()` for location-based emails:

```{r focal_filter_location_example}
focal_filter <- function(all_data, recipient_id) {
  config <- config::get()
  recipients <- read.csv(config$recipients_file, stringsAsFactors = FALSE)

  rec <- recipients[recipients$recipient_id == recipient_id, , drop = FALSE]
  if (nrow(rec) == 0) {
    stop("No recipient row for recipient_id = ", recipient_id)
  }

  # Each recipient row maps to a location of interest.
  loc <- rec$location_id[1]

  # Focal data now means all records in that location.
  focal_data <- subset(all_data, location_id == loc)

  focal_data
}
```

Once this is in place, `rf_render_single()` and `rf_render_all()` work as normal, but each email can now summarise all records from the recipient's location.

If your source data has coordinates instead of a `location_id`, you can apply a spatial filter in `focal_filter()` using polygons or bounding boxes from the recipient row.

## Customising Templates

- `templates/content.Rmd`: Defines content structure and where computed objects are shown.
- `templates/template.html`: Controls final page styling and layout wrapper.

Keep template edits small and test with `rf_render_single()` after each change.

## Viewing and Verifying Output

After generation, you can view and verify the content:

```{r view_content}
rf_view_content(batch_id = batch_id, recipient_id = 1)
```

```{r verify_batch}
rf_verify_batch(batch_id)
```

## Common First-Run Issues

- `meta_table.csv` missing: batch rendering did not complete.
- Template errors during render: test with `rf_render_single()` to isolate the failing recipient.
- Missing recipient output: check that `recipient_id` values match between recipients and data files.

## Next Step

After content renders cleanly, continue to the "Distributing Content" vignette to send output by email.
