---
title: "Generating Content"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generating Content}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(recorderFeedback)
```

# Generating Content

This vignette explains how to turn your loaded data into personalised feedback pages.
It is aimed at new users who have already completed the "Getting Data" steps.

## Workflow At A Glance

The content stage has three parts:

1. Optional computations on focal and background data.
2. Rendering one recipient for testing.
3. Rendering all recipients as a batch.

## Configuration

Content generation is controlled by `config.yml`. Key entries are:

- `computation_script_focal`: Script for computations on focal (recipient-specific) data.
- `computation_script_bg`: Script for background computations.
- `content_template_file`: RMarkdown template for rendering feedback.
- `html_template_file`: HTML template for styling output.

By default, both computation script fields point to `"scripts/computation.R"`.

```{r show_content_config}
config <- config::get()
config[c(
  "computation_script_focal",
  "computation_script_bg",
  "content_template_file",
  "html_template_file"
)]
```

## Computations

Computation scripts let you prepare summaries and metrics before rendering.
This is useful for totals, rankings, trends, and other values you want to reuse in templates.

In normal use, computations are executed automatically as part of rendering.
If you are building custom scripts, this is the core helper used internally:

```{r run_computations}
records <- read.csv(config$data_file)
computed <- rf_do_computations(config$computation_script_bg, records)
```

Your computation script should define `compute_objects(records_data)` and return an object (often a list) that can be used in templates.

## Rendering Content

Start by rendering a single recipient to check template logic before running a full batch.

```{r render_single}
# Use a known recipient_id from recipients_file
rf_render_single(recipient_id = 1)
```

Then run the whole batch:

```{r generate_batch}
batch_id <- "example_batch"
rf_render_all(batch_id)
```

## Customising Templates

- `templates/content.Rmd`: Defines content structure and where computed objects are shown.
- `templates/template.html`: Controls final page styling and layout wrapper.

Keep template edits small and test with `rf_render_single()` after each change.

## Viewing and Verifying Output

After generation, you can view and verify the content:

```{r view_content}
rf_view_content(batch_id = batch_id, recipient_id = 1)
```

```{r verify_batch}
rf_verify_batch(batch_id)
```

## Common First-Run Issues

- `meta_table.csv` missing: batch rendering did not complete.
- Template errors during render: test with `rf_render_single()` to isolate the failing recipient.
- Missing recipient output: check that `recipient_id` values match between recipients and data files.

## Next Step

After content renders cleanly, continue to the "Distributing Content" vignette to send output by email.
