---
title: "Distributing Content"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Distributing Content}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(recorderFeedback)
```

# Distributing Content

This vignette explains how to safely send generated feedback by email.
It is designed for new users who have already rendered a batch successfully.

## Before Sending Any Email

Confirm these prerequisites first:

1. You have run `rf_render_all(batch_id)`.
2. `renders/<batch_id>/meta_table.csv` exists.
3. `rf_verify_batch(batch_id)` completes without blocking errors.

## Configuration

Distribution settings are managed in your project's `config.yml` file. Key entries include:

- `mail_server`: SMTP server address.
- `mail_port`: SMTP port (default: 587).
- `mail_use_tls` / `mail_use_ssl`: Security options for email.
- `mail_username`, `mail_password`: Credentials for authentication.
- `mail_sender`, `mail_name`: Sender details.
- `mail_subject`: Subject line for feedback emails.
- `mail_test_recipient`: Address for test emails.
- `mail_creds`: Authentication mode (`"anonymous"` or `"envvar"`).
- `test_mode`: If `TRUE`, all messages are redirected to `mail_test_recipient`.
- `mail_retry_max`: Number of retries after first failed send attempt.
- `mail_retry_backoff_sec`: Base backoff in seconds (uses exponential backoff).
- `mail_rate_per_minute`: Maximum send attempts per minute.

```{r show_mail_config}
config <- config::get()
config[c(
  "test_mode",
  "mail_creds",
  "mail_server",
  "mail_port",
  "mail_sender",
  "mail_name",
  "mail_subject",
  "mail_test_recipient"
)]
```

## Dispatching Feedback

After generating feedback content, use `rf_dispatch_smtp()` to send emails to recipients. This function uses the configuration above to connect to your mail server and distribute feedback.

```{r dispatch_feedback, eval=FALSE}
batch_id <- "example_batch"
rf_dispatch_smtp(batch_id)
```

For a preflight check without sending any emails:

```{r dispatch_dry_run, eval=FALSE}
rf_dispatch_smtp(batch_id, dry_run = TRUE)
```

To continue a previously interrupted run and skip already successful sends:

```{r dispatch_resume, eval=FALSE}
rf_dispatch_smtp(batch_id, resume = TRUE)
```

For a safe first run, keep `test_mode: TRUE` in `config.yml`.
This sends all outputs to `mail_test_recipient` instead of real recipient addresses.

If `test_mode: FALSE`, you must explicitly confirm a live send:

```{r dispatch_live_confirm, eval=FALSE}
rf_dispatch_smtp(batch_id, confirm_live_send = TRUE)
```

## Customising Email Content

- Email body content comes from `content_template_file` and `html_template_file`.
- Sending format is controlled by `email_format` (usually `templates/email_format.R`).

## Verifying Distribution

After dispatch, you can verify which emails were sent and check for any errors:

```{r verify_batch}
rf_verify_batch(batch_id)
```

Inspect the generated dispatch files:

- `renders/<batch_id>/dispatch_log.csv`: One row per recipient send attempt.
- `renders/<batch_id>/dispatch_summary.csv`: Summary metrics for the run.

## Common First-Run Issues

- Authentication failure: review `mail_creds`, username/password, host, and port.
- TLS/SSL mismatch: check `mail_use_tls` and `mail_use_ssl` for your SMTP provider.
- Footer email mismatch error: generated file email does not match the meta table row.

## Summary

- Email distribution is fully configurable via `config.yml`.
- Use `rf_dispatch_smtp()` to send feedback to recipients.
- Keep `test_mode: TRUE` for dry runs, then switch to `FALSE` for live sending.

This approach helps you validate delivery safely before contacting real recipients.
