---
title: "Getting Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(recorderFeedback)
```

# Getting Data

This vignette is for first-time users of **recorderFeedback**. It explains how recipient data and observation data are loaded into your project in a way that can be repeated every reporting cycle.

## Before You Start

You should have:

- A project created with `rf_init()`.
- A `config.yml` file in your project root.
- The package loaded with `library(recorderFeedback)`.

If you have not initialised a project yet, run:

```{r init_project}
rf_init("my_feedback_project")
```

Then work inside that folder so relative paths in `config.yml` resolve correctly.

## Configuration

Data input is controlled by your project's `config.yml`. The most important fields are:

- `recipients_file`: Path to your recipients data (e.g., `"data/recipients.csv"`).
- `recipients_script`: Script for loading recipients (e.g., `"scripts/get_recipients.R"`).
- `data_file`: Path to your records/observations data (e.g., `"data/data.csv"`).
- `data_script`: Script for loading records (e.g., `"scripts/get_data.R"`).

Each `*_script` should create or update the corresponding `*_file`.

```{r load_config}
config <- config::get()
config[c("recipients_script", "recipients_file", "data_script", "data_file")]
```

## Loading Recipients

`rf_get_recipients()` runs the script defined in `recipients_script`.
That script should write a recipients table to `recipients_file`.

At minimum, recipients data should include:

- `recipient_id`
- `name`
- `email`

```{r get_recipients}
rf_get_recipients()
recipients <- read.csv(config$recipients_file)
knitr::kable(head(recipients))
```

## Loading Records

`rf_get_data()` runs the script defined in `data_script`.
That script should write your raw records to `data_file`.

Your records must include `recipient_id` so each record can be linked to a recipient.

```{r get_data}
rf_get_data()
records <- read.csv(config$data_file)
knitr::kable(head(records))
```

## Validate Inputs Early

Run validation immediately after loading data. This catches missing files, missing columns, and recipient/data mismatches before rendering.

```{r verify_data}
rf_verify_data(verbose = TRUE)
```

## Common First-Run Issues

- `Data file has not been updated`: your `scripts/get_data.R` script did not write to `config$data_file`.
- `Recipient file has not been updated`: your `scripts/get_recipients.R` script did not write to `config$recipients_file`.
- Missing column errors: ensure required columns are named exactly (`recipient_id`, `name`, `email`).

## Next Step

Once data loading works, continue to the "Generating Content" vignette to render recipient-specific reports.
